UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio and Reconfigurable Intelligent Surface

### 2022-08-14 main.tex
:pencil: Add transition to UniScatter

				\label{eq:reflection_coefficient}

@@

@@

	\begin{subsection}{RIS: Channel Reconfiguration}
		% \gls{ris} elements assist legacy transmission by \emph{deterministically choosing phase shifts} based on relevant \gls{csi}. For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding phase shift $\theta_m$ by \cite{Wu2018}
		% \gls{ris} involves numerous
		\gls{ris} typically involves a planar antenna array or metasurface of numerous metamaterial units as a passive channel reconfigurator.
		% By \emph{adaptively deciding} the reflection pattern, each reflecting element alters the phase of reflected signal for constructive/destructive superposition at the receiver.
		By \emph{adaptively choosing} the reflection pattern, each reflecting element alters the phase of scattered signal for constructive/destructive superposition at the receiver.
		% Compared with backscatter nodes of \gls{bc}/\gls{sr}, \gls{ris} elements employ deterministic reflection pattern priorly known at transmitter and receiver.
		% Reflecting elements of \gls{ris} assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
		For each unit with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
		\begin{equation}
			\Gamma_m = \beta_m \exp(j \theta_m),
		\end{equation}
		where $0 \le \beta_m \le 1$ is the overall amplitude scattering ratio of state $m$.
		% Based on relevant \gls{csi}
	\end{subsection}
	% Tags periodically switch between different states to perform backscatter modulation.
	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
	% \begin{equation}
	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
	% 	\label{eq:backscatter_modulation}
	% \end{equation}
	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
	% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.

	\begin{subsection}{UniScatter: Bridge and Generalization}
		% TODO compare BC, SR and IRS
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
			}
			\\
			\subfloat[Time Block]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_block.tex}
				}
			}
			\caption{
				Input probability distribution and time block structure of \gls{sr}, \gls{ris}, and UniScatter.
				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
				Within channel coherence time, UniScatter nodes semi-randomly select reflection state for each backscatter block, with guidance from input probability distribution.
			}
			\label{fi:uniscatter}
		\end{figure}
		% ! Passive backscatter nodes harvest energy from and modulate information over surrounding \gls{rf} signals.
		% As shown in Fig. \subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
		% Its equivalent circuit is presented in Fig. \subref*{fi:equivalent_circuit}.
		% When illuminated, the node absorbs a portion of the impinging wave for information decoding and/or energy harvesting \cite{Kim2021a}, and backscatters the remaining as \emph{structural} and \emph{antenna} components.
		% The former consistently contributes to environment multipath and can be modelled by channel estimation \cite{Boyer2014}, while the latter depends on antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
		% Fig. \subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ states.

		% ? For a passive node with finite states, is it possible to unify backscatter modulation and channel reconfiguration by proper selection of reflection coefficient?
		UniScatter nodes simultaneously transmit and assist by \emph{adaptive input distribution design} based on primary and (cascaded) backscatter \gls{csi}.
		% The reflection pattern is neither fully random nor fully deterministic, but flexibly distributed to balance backscatter encoding and passive beamforming.
		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter semi-randomly selects reflection state for each backscatter block with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.} In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming. \gls{sr} and \gls{ris} can be regarded as extreme cases of UniScatter, where node input distribution boils down to uniform and deterministically biased, respectively.
		Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter nodes semi-randomly select reflection state for each backscatter block, with \emph{guidance of input probability $P(\Gamma_m)$} for state $m$. In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
		% \gls{sr} and \gls{ris} can be regarded as extreme cases of UniScatter nodes, where node input distribution boils down to uniform and deterministic, respectively.
		% flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
		% UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
		% % Based on \gls{csi}, UniScatter adapts the reflection state distribution to unify data transmission and channel reconfiguration.
		% \gls{sr} and \gls{ris} can be regarded as its extreme cases, where node input distribution boils down to uniform and deterministically biased, respectively.
		% Within channel coherence time, UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
		\begin{remark}
			Compared to conventional \gls{ris} literatures that optimize phase shifts under unit-module constraint, UniScatter nodes start from predefined reflection coefficients and designs their input distribution under sum-probability constraint to achieve flexible primary-backscatter tradeoff.
		\end{remark}
		% Next, we will discuss the input design in a UniScatter-enabled network.
		% consider a UniScatter-aided system to evaluate
	\end{subsection}
\end{section}

\begin{section}{UniScatter}
	\begin{subsection}{System Model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.8\columnwidth}
			\footnotesize{
				\import{assets/illustration/}{uniscatter_network.eps_tex}
			}
			\caption{A UniScatter-enabled single-user multi-node network.}
			\label{fi:uniscatter_network}
		\end{figure}
		% As shown in Fig. \ref{fi:uniscatter_network}, we propose a UniScatter-enabled single-user multi-node network where the spectrum, energy and infrastructures are shared by two coexisting systems.
		% UniScatter-enabled single-user multi-node \gls{miso} network where multiple UniScatter nodes ride over a point-to-point transmission to
		As shown in Fig. \ref{fi:uniscatter_network}, we propose a UniScatter-enabled single-user multi-node \gls{miso} network where two coexisting systems share spectrum, energy and infrastructures.
		% In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
		% In the primary point-to-point system, a $Q$-antenna \gls{ap} transmit to a single-antenna user while assisted by $K$ nearby single-antenna UniScatters.
		The primary point-to-point transmission from a $Q$-antenna \gls{ap} to a single-antenna user is assisted by $K$ nearby single-antenna UniScatter nodes.
		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, $K$ nearby single-antenna UniScatter nodes modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
		For simplicity, we consider a quasi-static block fading model where channels remain constant within coherence interval while vary independently between consecutive blocks.
		% Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol period is $N \in \mathbb{Z}_{++}$ times the primary symbol period.
		Due to physical constraints on load switching, we assume the backscatter symbol period is $N \gg 1$ times longer than primary and consider integer $N$ without loss of generality.
		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.%
		\footnote{
			Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
			One possibility is the \gls{ap} sends training pilots, the tags respond in predefined manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.
		}
		Besides, we omit the signal reflected by two or more times\cite{Wu2019} and ignore the time difference of arrival from different paths\cite{Guo2019b}.

@@

		% Therefore, the weighted sum information function, marginal information function, and mutual information of primary and backscatter links are respectively given by
		% \begin{align}
		% 	I(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
		% 	 & \triangleq \rho I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
		% 	I_k(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})
		% 	 & \triangleq \rho I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
		% 	I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
		% 	 & \triangleq \rho I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
		% \end{align}
		% where $\rho \in [0,1]$ represents the priority of the primary link.
	\end{subsection}
\end{section}

>>>>

				\label{eq:reflection_pattern_antenna}

@@

				\label{eq:reflection_pattern_metamaterial}

@@

	\begin{subsection}{RIS: Channel Reconfiguration}
		\gls{ris} typically involves a planar antenna array or metasurface of numerous metamaterial units as a passive channel reconfigurator.
		By \emph{adaptively choosing} the reflection pattern, each reflecting element alters the phase of scattered signal for constructive/destructive superposition at the receiver.
		For each unit with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
		\begin{equation}
			\Gamma_m = \beta_m \exp(j \theta_m),
			\label{eq:passive_beamforming}
		\end{equation}
		where $0 \le \beta_m \le 1$ is the overall amplitude scattering ratio of state $m$.
	\end{subsection}

	% \begin{subsection}{Opportunities and Challenges}
	\begin{subsection}{Opportunities}
		We have seen conventional scattering applications as \gls{bc}, \gls{sr} and \gls{ris} using the reflection pattern \eqref{eq:reflection_pattern_antenna}, \eqref{eq:reflection_pattern_metamaterial} for either backscatter modulation \eqref{eq:backscatter_modulation} or passive beamforming \eqref{eq:passive_beamforming}.
		A natural but critical question is, for a given scatterer with pre-determined reflection pattern set, \emph{can we softly bridge backscatter modulation and passive beamforming by appropriate reflection design?}
		This question is answered in Section \ref{se:uniscatter}.
	\end{subsection}
\end{section}

\begin{section}{UniScatter}
	\begin{subsection}{UniScatter Nodes}
		% TODO compare BC, SR and IRS
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
			}
			\\
			\subfloat[Time Block]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_block.tex}
				}
			}
			\caption{
				Input probability distribution and time block structure of \gls{sr}, \gls{ris}, and UniScatter.
				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
				Within channel coherence time, UniScatter nodes semi-randomly select reflection state for each backscatter block, with guidance from input probability distribution.
			}
			\label{fi:uniscatter}
		\end{figure}
		% ! Passive backscatter nodes harvest energy from and modulate information over surrounding \gls{rf} signals.
		% As shown in Fig. \subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
		% Its equivalent circuit is presented in Fig. \subref*{fi:equivalent_circuit}.
		% When illuminated, the node absorbs a portion of the impinging wave for information decoding and/or energy harvesting \cite{Kim2021a}, and backscatters the remaining as \emph{structural} and \emph{antenna} components.
		% The former consistently contributes to environment multipath and can be modelled by channel estimation \cite{Boyer2014}, while the latter depends on antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
		% Fig. \subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ states.

		% ? For a passive node with finite states, is it possible to unify backscatter modulation and channel reconfiguration by proper selection of reflection coefficient?
		UniScatter nodes simultaneously transmit and assist by \emph{adaptive input distribution design} based on primary and (cascaded) backscatter \gls{csi}.
		% The reflection pattern is neither fully random nor fully deterministic, but flexibly distributed to balance backscatter encoding and passive beamforming.
		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter semi-randomly selects reflection state for each backscatter block with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.} In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming. \gls{sr} and \gls{ris} can be regarded as extreme cases of UniScatter, where node input distribution boils down to uniform and deterministically biased, respectively.
		Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter nodes semi-randomly select reflection state for each backscatter block, with \emph{guidance of input probability $P(\Gamma_m)$} for state $m$. In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
		% \gls{sr} and \gls{ris} can be regarded as extreme cases of UniScatter nodes, where node input distribution boils down to uniform and deterministic, respectively.
		% flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
		% UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
		% % Based on \gls{csi}, UniScatter adapts the reflection state distribution to unify data transmission and channel reconfiguration.
		% \gls{sr} and \gls{ris} can be regarded as its extreme cases, where node input distribution boils down to uniform and deterministically biased, respectively.
		% Within channel coherence time, UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
		\begin{remark}
			Compared to conventional \gls{ris} literatures that optimize phase shifts under unit-module constraint, UniScatter nodes start from predefined reflection coefficients and designs their input distribution under sum-probability constraint to achieve flexible primary-backscatter tradeoff.
		\end{remark}
		% Next, we will discuss the input design in a UniScatter-enabled network.
		% consider a UniScatter-aided system to evaluate
	\end{subsection}

	\begin{subsection}{System Model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.8\columnwidth}
			\footnotesize{
				\import{assets/illustration/}{uniscatter_network.eps_tex}
			}
			\caption{A UniScatter-enabled single-user multi-node network.}
			\label{fi:uniscatter_network}
		\end{figure}
		% As shown in Fig. \ref{fi:uniscatter_network}, we propose a UniScatter-enabled single-user multi-node network where the spectrum, energy and infrastructures are shared by two coexisting systems.
		% UniScatter-enabled single-user multi-node \gls{miso} network where multiple UniScatter nodes ride over a point-to-point transmission to
		As shown in Fig. \ref{fi:uniscatter_network}, we propose a UniScatter-enabled single-user multi-node \gls{miso} network where two coexisting systems share spectrum, energy and infrastructures.
		% In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
		% In the primary point-to-point system, a $Q$-antenna \gls{ap} transmit to a single-antenna user while assisted by $K$ nearby single-antenna UniScatters.
		The primary point-to-point transmission from a $Q$-antenna \gls{ap} to a single-antenna user is assisted by $K$ nearby single-antenna UniScatter nodes.
		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, $K$ nearby single-antenna UniScatter nodes modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
		For simplicity, we consider a quasi-static block fading model where channels remain constant within coherence interval while vary independently between consecutive blocks.
		% Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol period is $N \in \mathbb{Z}_{++}$ times the primary symbol period.
		Due to physical constraints on load switching, we assume the backscatter symbol period is $N \gg 1$ times longer than primary and consider integer $N$ without loss of generality.
		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.%
		\footnote{
			Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
			One possibility is the \gls{ap} sends training pilots, the tags respond in predefined manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.
		}
		Besides, we omit the signal reflected by two or more times\cite{Wu2019} and ignore the time difference of arrival from different paths\cite{Guo2019b}.

@@

		% Therefore, the weighted sum information function, marginal information function, and mutual information of primary and backscatter links are respectively given by
		% \begin{align}
		% 	I(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
		% 	 & \triangleq \rho I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
		% 	I_k(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})
		% 	 & \triangleq \rho I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
		% 	I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
		% 	 & \triangleq \rho I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
		% \end{align}
		% where $\rho \in [0,1]$ represents the priority of the primary link.
	\end{subsection}
	\label{se:uniscatter}
\end{section}
